---
output:
  pdf_document: default
  html_document: default
---

 
# Southern Farm Bureau Casualty Insurance Company Symbols Modelling 
<br />
*`r input$name`* <br />   
*`r as.character(format(Sys.Date(), format="%B %d, %Y"))`*

<br />

###1. Summary Statistics

This report was created using the `r input$dataset` data set.  The dependent variable in my analysis is `r input$dv` and independent variable in my analysis is `r input$iv`. 

<br />

The summary statistics of `r input$dv` and `r input$iv` appear below. 
```{r summary, echo=FALSE}
  mlb11 <- datasetInput()
  temp <- cbind(mlb11[input$dv], mlb11[input$iv])
  summary(temp)
```

`r input$text_summary` 

<br />

###2. Histograms 

The histograms of `r input$dv` and `r input$iv` appear below. <br />
<br />
<br />
```{r hist_dv, echo=FALSE}
   x    <- VehiclesSymbolDatNew[,input$dv]  
  bins <- seq(min(x), max(x), length.out = input$bins_dv + 1)
 
    hist(x, breaks = bins, col = 'green', border = 'blue', main = 'Dependent Variable', xlab = input$dv)
```

`r input$text_hist_dv`

```{r hist_iv, echo=FALSE}
   x    <- VehiclesSymbolDatNew[,input$iv]  
 bins <- seq(min(x), max(x), length.out = input$bins_iv + 1)

  hist(x, breaks = bins, col = 'green', border = 'blue', main = 'Independent Variable', xlab = input$iv)
```

`r input$text_hist_iv`


<br />

###3. Scatter Plot 

A scatter plot of `r input$dv` and `r input$iv` appears below.  <br />
<br />

```{r scatter, echo=FALSE}

  plot(VehiclesSymbolDatNew[,input$iv],VehiclesSymbolDatNew[,input$dv],
       xlab = input$iv, ylab = input$dv,  main = "Scatter Plot of Independent and Dependent Variables", pch = 16, 
       col = "black", cex = 1) 
  
  abline(glm(VehiclesSymbolDatNew[,input$dv]~VehiclesSymbolDatNew[,input$iv]), col="grey", lwd = 2) 
```

`r input$text_scatter`



###5. Model

A bivariate  model predicting `r input$dv` with `r input$iv` appears below. 



<br />


###6. Model Evaluation
```{r}
 head(cbind( Train_MSE=mean((VehiclesSymbolDatNew$LossCostMetric -   model()$fitted.values)^2),AICValue=AICtweedie(model(),k=2)))
```



### 7. Model Factors

```{r}
 options(scipen = 999)
 round(exp(coef(model())),digits=4)
   
```


###8. Slope Plots

```{r}
   par(mfrow = c(3,4),bg = 'olivedrab1')
    termplot(model(),main="Slope of Selected Predictor") 
    
```


###9. Comparative Fitted Model Plots 
```{r text_AvgGraph, echo=FALSE}
 par(mfrow = c(1,1))
      datasetInputfit= cbind(VehiclesSymbolDatNew[,], FittedLossCost=model()$fitted.values)
  
      AggtableObsFit<- aggregate(cbind(LossCostMetric,FittedLossCost ) ~ VehiclesSymbolDatNew[,input$iv], data = datasetInputfit, mean)
      counts <- table(datasetInputfit[,input$iv])
      counts <- prop.table(counts)
      par(mar=c(5, 4, 4, 6) + 0.1)
      
      barplot(counts, pch=15,  xlab=" ", ylab=" ", ylim=c(0,max(counts)+.1), 
              axes=FALSE,  col="green")
      mtext("Proportion",side=4,col="green",line=4) 
      axis(4,  col="green",col.axis="green",las=1)
      par(new=TRUE)
       plot(1:length(AggtableObsFit$LossCostMetric),AggtableObsFit$LossCostMetric, col="red", type="b",pch=19,lwd=2, ylab=" ", xlab=" ",xaxt = "n",
            ylim=c(min(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost),max(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost)))
      par(new=TRUE)
      plot(1:length(AggtableObsFit$FittedLossCost),AggtableObsFit$FittedLossCost, col="blue", type="b",pch=18,xlab=" ", ylab=" ",lwd=2, axes=FALSE,xaxt = "n",
           ylim=c(min(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost),max(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost)))
      legend("topleft", legend=c("Observed Average", "Fitted Model Average"),
             col=c("red", "blue"), lty=1:3, cex=1)
      grid(nx=NULL,ny=NULL)

  
```

`input$text_AvgGraph`



###10. Score Model Graph  

```{r text_ScoreGraph, echo=FALSE}
   par(mfrow = c(1,1))
    
    datasetInputfit= cbind(VehiclesSymbolDatNew[,], FittedLossCost=model()$fitted.values)
    datasetInputfit$ScoreGrp <- cut(datasetInputfit$FittedLossCost, breaks=c(0,100,150,200,250,300,400,500,600,800,5000), right = FALSE,dig.lab=6)  
    datasetInputfit$ScoreGrp<-ifelse(datasetInputfit$ScoreGrp=='[0,100)',1,datasetInputfit$ScoreGrp)
    
    
    AggtableObsFit<- aggregate(cbind(LossCostMetric,FittedLossCost ) ~ datasetInputfit$ScoreGrp, data = datasetInputfit, mean)
    counts <- table(datasetInputfit$ScoreGrp)
    counts <- prop.table(counts)
    par(mar=c(5, 4, 4, 6) + 0.1)
    
    barplot(counts, pch=15,  xlab=" ", ylab=" ", ylim=c(0,max(counts)+.1), 
            axes=FALSE,  col="green")
    mtext("Proportion",side=4,col="green",line=4) 
    axis(4,  col="green",col.axis="green",las=1)
    par(new=TRUE)
    plot(1:length(AggtableObsFit$LossCostMetric),AggtableObsFit$LossCostMetric, col="red", type="b",pch=19,lwd=2, ylab=" ", xlab=" ",xaxt = "n",
         ylim=c(min(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost),max(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost)))
    par(new=TRUE)
    plot(1:length(AggtableObsFit$FittedLossCost),AggtableObsFit$FittedLossCost, col="blue", type="b",pch=18,xlab=" ", ylab=" ",lwd=2, axes=FALSE,xaxt = "n",
         ylim=c(min(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost),max(AggtableObsFit$LossCostMetric,AggtableObsFit$FittedLossCost)))
    legend("topleft", legend=c("Observed Average", "Fitted Model Average"),
           col=c("red", "blue"), lty=1:3, cex=1)
    grid(nx=NULL,ny=NULL)

```

`input$text_ScoreGraph`



